Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-08-23 figures_Paper1/spec_filling_mu1_v_0.4_0.8_O_5_11_e.tex
Final version 23.08.2022

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega/t^{*}$},
ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0, 
    /tikz/.cd}
]

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega/t^{*}$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:0,0.1)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]

>>>>

\nextgroupplot[
xmin=-15.,      
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
ylabel={$A(\omega)$},
legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0, 
    /tikz/.cd}
]

@@

\nextgroupplot[
xmin=-15.,     
xmax=15., 
ymin=0.00, 
ymax=0.09,   
minor tick num=1, 
grid=both,
xlabel={$\omega$},
% ylabel={$A(\omega)/t^{*-1}$},
legend style={at={(axis cs:-8.8,0.017)},anchor=north,mark options={scale=1.0},/tikz/every odd column/.append style={column sep=0.5mm},legend columns=1},
legend cell align=left,
clip mode=individual,
clip marker paths=true, 
xtick={-15,-10,-5,0,5,10,15},
ytick={0.00,0.03,0.06,0.09},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012},
% yticklabels={\smash{\raisebox{0.1\height}{0}},0.002,0.004,0.006,0.008,0.01,0.012,\smash{\raisebox{-0.8\height}{5}}},
x tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd},
y tick label style={
    /pgf/number format/.cd,
    fixed,
    fixed zerofill,
    precision=0,
    /tikz/.cd}
]
